Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-04-25 paper.tex

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/simple-methods-5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\columnwidth]{figures/simple-methods-5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/simple-methods-6vs7}
        \end{subfigure}
	\caption{Average performance of Complete Columns methods in three different condition pairs}
	\label{fig:simple-methods}
\end{figure}
%-----------------------------------------------------------
\subsection{ALS with biases}

\subsubsection{RandomFile Numbers(Uniform) - RFNU}
Figure~\ref{fig:RFNU method} represents
the accuracy graph of RFNU method with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNU-ALS-Bias-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNU-ALS-Bias-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNU-ALS-Bias-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of RFNU methods in three different condition pairs}
        \label{fig:RFNU method}
\end{figure}
\subsubsection{RNFT-L}
Figure~\ref{fig:RFNT-L method} represents
the accuracy graph of RFNT-L method with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-L-ALS-Bias-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-L-ALS-Bias-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-L-ALS-Bias-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of RFNT-L methods in three different condition pairs}
        \label{fig:RFNT-L method}
\end{figure}
\subsubsection{RFNT-S}
Figure~\ref{fig:RFNT-S method} represents
the accuracy graph of RFNTS method with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-S-ALS-Bias-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-S-ALS-Bias-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-S-ALS-Bias-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of RFNT-S methods in three different condition pairs}
        \label{fig:RFNT-S method}
\end{figure}
%-----------------------------------------------------------
% Present your results: accuracy, ROC curves, transparency matrix, factors.

>>>>

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/simple-methods-5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\columnwidth]{figures/simple-methods-5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/simple-methods-6vs7}
        \end{subfigure}
	\caption{Average performance of all methods in three different condition pairs}
	\label{fig:simple-methods}
\end{figure}
%-----------------------------------------------------------
\subsection{ALS with biases}

\subsubsection{RandomFile Numbers(Uniform) - RFNU}
Figure~\ref{fig:RFNU method} represents
the accuracy graph of RFNU method with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNU-ALS-Bias-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNU-ALS-Bias-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNU-ALS-Bias-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of RFNU methods with considering Bias in three different condition pairs}
        \label{fig:RFNU method}
\end{figure}
\subsubsection{RNFT-L}
Figure~\ref{fig:RFNT-L method} represents
the accuracy graph of RFNT-L method with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-L-ALS-Bias-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-L-ALS-Bias-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-L-ALS-Bias-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of RFNT-L methods  with considering Bias in three different condition pairs}
        \label{fig:RFNT-L method}
\end{figure}
\subsubsection{RFNT-S}
Figure~\ref{fig:RFNT-S method} represents
the accuracy graph of RFNTS method with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-S-ALS-Bias-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-S-ALS-Bias-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-S-ALS-Bias-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of RFNT-S methods  with considering Bias in three different condition pairs}
        \label{fig:RFNT-S method}
\end{figure}
%-----------------------------------------------------------
% Present your results: accuracy, ROC curves, transparency matrix, factors.
